Reproducible Research : Peer Assessment 1
---------------------------------------------------------------------
---------------------------------------------------------------------

## Load and preposs the data

```{r}
da=read.csv("activity.csv")
da$date=as.Date(da$date, "%Y-%m-%d")
summary(da)

```


## Mean total numer of steps taken per day
### 1. Calculate the total number of steps taken per day
``` {r}
mean(da$steps, na.rm=T)

```

### 2. Histogram of the total number of steps taken each day
``` {r}
da.agg= aggregate(steps ~ date, data=da, FUN=sum)
hist(da.agg$steps)
```

### 3. Mean and Median of the total number of steps per day
``` {r}
mean(da.agg$steps)
median(da.agg$steps)
```



## Average daily activity pattern
### 1. Make a time series plot
```{r}
library(ggplot2)
da.ave=aggregate(steps ~ interval, data=da, FUN=mean)
ggplot(aes(x=interval, y=steps), data=da.ave) + geom_line()
```

### 2. Maximum number of steps
``` {r}
max.index=which.max(da.ave$steps)
da.ave[max.index, c("interval")]
```

## Input missing values
### 1. total number of missing values in the dataset
```{r}
 nrow(subset(da, is.na(steps))) #missing steps
 nrow(subset(da, is.na(interval))) #missing intervals
```
### 2. Fill in all of the missing values
```{r}
impute.mean=function(x) {
  z=mean(x, na.rm=T)
  x[is.na(x)]=z
  return(x)
}

```

### 3. Create a new dataset which is equal to the original dataset but with the missing data filled in
```{r}
da.new=da
da.new$steps=impute.mean(da.new$steps)
```

### 4. Make a histogram of the total number of steps taken each day 
```{r}
da.new.agg= aggregate(steps ~ date, data=da.new, FUN=sum)
hist(da.new.agg$steps)
mean(da.new.agg$steps)
median(da.new.agg$steps)
```

###... and report the mean and median total numbers taken per day.
```{r}
mean(da.new.agg$steps)
median(da.new.agg$steps)
```

## Are there differences in activity patterns betw weekdays and weekends
### 1. create a new factor variable in the dataset with two levels - "weekday" and "weekend"
```{r}
da.new$dow=weekdays(da.new$date)
da.new$weekday=as.factor(ifelse(da.new$dow %in% c("Saturday", "Sunday"), "weekend", "weekday"))
```

### 2. Make a panel plot
```{r}

da.new.ave=aggregate(steps ~ interval + weekday, data=da.new, FUN=mean)
ggplot(aes(x=interval, y=steps), data=da.new.ave) + geom_line() + facet_grid(weekday ~ .)

```